---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) [![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)

# calibreinterface

The goal of calibreinterface is to read information from your local calibre ebook manager. We read from the database, never write, because that might corrupt your calibre instance. 

## Installation

You can install the released version of calibreinterface from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("calibreinterface")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("RMHogervorst/calibreinterface")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```


Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.
